The Current State of Test-First vs. Test-Last Testing Draft

### 2013-11-08 Paper_Draft.tex
Commiting paper.

\title{Agile Testing Four Page Draft}

@@

\author{
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
\alignauthor
Chris M. Thomas\\
	\affaddr{Division of Science and Mathematics}\\
	\affaddr{University of Minnesota, Morris}\\
	\affaddr{Morris, Minnesota, USA 56267}\\
	\email{thom3706@morris.umn.edu}
}

\maketitle
\begin{abstract}
\mycomment{Needs to be written!}

\mycomment{passages or ideas worth putting into my abstract below}

When it comes to software development perhaps one of the most important and time consuming processes is that of software testing.  In fact, some early studies on software testing estimated that software testing could consume fifty percent or more of development costs for a product.

Currently there is much debate in the testing world about whether or not test first testing or test last testing is superior and what advantages one type of testing may offer over the other.  The goal of this paper is to therefore attempt to resolve this debate as much as possible by analyzing research data in the field concerning the advantages and disadvantages of each of these testing methods.

Due to these issues new methods are starting to appear in the agile community that contain some of TDD's main tenets but have shifted enough away from TDD at some fundamental level that they are starting to receive their own names and classifications. 
\end{abstract}

@@

\section{Introduction}
When it comes to software development, perhaps one of the most important and time consuming processes is software testing.  In fact, some early studies on software testing estimated that it could consume fifty percent or more of development costs for a product ~\cite{Bertolino;2007}.  because of this businesses over time have become increasingly interested in attempting to optimize testing to reduce development costs.

Although there are many testing methods that currently exist two particular testing methods are currently very popular: test-last testing and test-first testing.  Test-last testing, used mostly in process oriented development, is a testing method where testing is done after the software code has been written to ensure that the code works correctly.  Test-first testing, used mostly in interval or sprint oriented development, is a testing method where testing is done before the software code is written to ensure that the future code meets certain requirements.

Currently, there is much debate in the testing community about whether or not test first or test last testing is superior.  The goal of this paper is to attempt to give an overview of the current state of this debate by analyzing current research data concerning the advantages and disadvantages of each of these testing methods.  Also because research often lags behind current implementations and the field of test first testing is currently changing due to its relatively new implementation this paper will also explore where new test first methods are going and compare them to the research given.  This paper will therefore discuss the advantages and disadvantages of test first testing versus test last testing and explore new emerging test-first methodologies in an attempt to determine the applicability of each methodology.

The rest of the paper is divided into four sections which will discuss the specific ideas above in more detail. In section two of the paper we will discuss what software testing is and current software development models with their supporting testing methods: test-first and test-last testing.  In section three we will provide an analysis of the data explaining the potential advantages and disadvantages of test first testing compared to test last testing.  In section four we will go over new test first based testing methodologies and in section five we will state our conclusions and suggestions for further research in the field.

@@

When it comes to judging the effectiveness of certain testing methods it is important to note that there is no one standard quantitative measurement.  Because of this many different types of measurement are used to attempt to prove that one testing methodology is better then another.  Although there are many different attributes that are used for arguing the superiority of one method over another we will only focus on three attributes that are commonly found throughout research; code coverage, time, and code correctness.  Code coverage refers to how many lines of code percent-wise are currently being tested. For example, if I write a test with 70\% test coverage it means that 70\% of the lines of code I wrote are being tested.  Time simply means how long it takes to write or run the actual tests.  Code correctness refers to how many errors are found within code after it is considered finished.  These three attributes are popular to use because they can be quantitatively measured and are considered important within the testing community.

@@

Test last testing is currently a popular testing method and is usually the first testing method that people tend to implement.  Test Last testing is the practice of writing tests after code has been written that check the functionality of their code.  These tests are then used to check the written code for any potential errors which are then fixed by the developer until no errors are found by the tests.  Test last testing is considered simple to implement and can allow the programmer to focus on writing tests based on areas of his code that he may be concerned about.

@@

In the late 1990s some software developers started to criticize the sequence-oriented waterfall model, complaining that it was too brittle and inflexible to meet the demands of the standard customer.  In response to these critiques of the waterfall model a new model for developing software emerged, the agile development model.  This new development model, based on the tenets of the agile manifesto \mycomment{cite manifesto here!}, promoted the idea that all actions of development should not occur in an ordered sequence but in a series of time-boxed iterations where in each iteration setting requirements, design, implementation and testing would occur simultaneously.  The goal of each iteration is to produce a demonstrable working product to show a customer and receive feedback on the product.  Some current development practices that are considered agile are Extreme Programming and Scrum.

Due to the changes in Agile programming test-last testing was pushed aside in favor of a new style known as test-first testing.  In 1996 \mycomment{might be 2001} with the release of the agile development practice Extreme Programming, the idea of test first testing, implemented in test driven development, started to become popular for the first time ~\cite{Hammond:2012}. Test-first testing is the practice of writing tests before code has been written and then writing code to make the tests pass.  It should be noted that since tests occur before development test-first testing tends to be heavily linked to development methods and thus the most common test-first models also include development elements as well.

The most well known and most used test-first model is that of test driven development or TDD for short.  In its current use in the field the phrase TDD is mostly used as a blanket term for any sort of development practice that uses test-first testing to drive code development. That being said it is important to note that although TDD has been turned into a vague term in this paper we will focus more on its original specific definition.

\section{Analysis of TDD}
\subsection{TDD Stances and Data}
Currently, TDD is the most popular testing method in the Agile community.  Many supporters of TDD claim that it reduces overall time spent on a product, improves test coverage, and increases overall code quality.  More importantly there exists data to back up some of these claims.  for example, in the experiment documented by ~\cite{Lemos:2012}, it was noted that on average TDD methodologies increased code coverage by 40\% compared to conventional testing methods.  Another study, documented in ~\cite{Hellman:2012} also suggested some positive traits about TDD by claiming some research showed that TDD practices could reduce effort by up to 27\%. Studies in articles ~\cite{Hellman:2012, Hammond:2012, Kettunen:2010} acknowledged multiple studies that empirically showed at least a marginal increase in product quality when TDD was implemented.  By looking at this data alone it would be relatively easy to see why TDD has such a positive image in industry and academia.

That being said, TDD also has many detractors as well who would tell you that TDD actually increases time spent on a product while not increasing overall code quality. This side also has a fair bit of research backing its opinion.  For example, in ~\cite{Lemos:2012} the same study that showed that TDD increased test coverage by 40\%, it was noted that TDD took significantly more time to implement then conventional testing and did not actually increase code quality. Also, the same study that found research showing the TDD could reduce effort by up to 27\% found other research that suggested that TDD actually increased the effort by two fold ~\cite{Hellman:2012}. It is also worth noting that articles ~\cite{Hammond:2012, Kettunen:2010} also have data and reports arguing that TDD takes more time then conventional testing.  What is perhaps troubling about the data given here is that most of it directly contradicts the data given in the first paragraph.  This suggests an interesting paradox where even though data given on TDD is statistically significant it is decidedly inconclusive.

\subsection{Analysis of Conflicting Data}
Even though the data surrounding TDD is inconclusive as a whole it should still be noted that information can still be extracted from it.  This is especially true because many of the results were statically significant meaning that some sort of meaningful data was obtained.   
Because most of the data was statistically sound it may be worth considering not that the data was faulty but perhaps that the studies contained potentially key differences from one another.  Thus it may be useful to us to try to understand why the data may be so conflicting as it may lead to useful insights about TDD indirectly.

One of the largest issues for summarizing the effectiveness of TDD is the field itself is very broad.  It is important to note that while I specifically defined the original ideas and methodologies of the original idea of TDD, TDD itself has become an umbrella term that has been used to describe a massive array of different testing practices.  This diversity may help explain why we are getting differing results because the TDD practice in one study may be extraordinary different from the TDD practice in another study.  It is worth noting that in ~\cite{Hammond:2012} a major issue with many TDD research papers was the absence of how the TDD process was implemented. This is a major issue in studying the field of TDD because it is hard to tell if people used similar or different methods of TDD to obtain their results.

Another issue for understanding the effectiveness of TDD that many TDD researchers have run into is that TDD is actually a difficult process to implement correctly.  There were many testimonies throughout various articles ~\cite{Hammond:2012, Hellman:2012, Kettunen:2010} of industry professionals finding the TDD process to be much more difficult to implement correctly compared to traditional testing frameworks.  Also, many articles on the analysis of TDD at some point brings up the topic of the complexity of TDD. This acknowledgement of complexity is important as it may suggest a result bias in TDD experiments based on the skill level of the participants as less experienced participants may be significantly less likely to implement TDD in an efficient or successful manner while more experienced participants may have more success.  In one study at a college, although not significantly analyzed due to a lack of participants, it was noted that Alumni who used TDD produced overall better quality code compared to their conventional testing Alumni counterparts while current students in the college showed almost no difference in code quality between TDD and conventional test methods ~\cite{Lemos:2012}.  This potential bias would wreck havoc on TDD data conclusiveness as a whole as the two major participant types for TDD experiments are industry professionals and college students who have vast gaps in experience difference.

Overall it is very hard to draw conclusions on the effectiveness of TDD. Out of all the data out there there is really only one data point that seems to be incontrovertible which is the fact that TDD always seems to increase overall code coverage.  Perhaps another conclusion that can be made is that TDD seems to produce no worse code quality then traditional waterfall testing.  Also there are some implications from potential confounding factors that not all TDD methods are created equal and experience may play a large role in TDD effectiveness. Everything else on the effectiveness of TDD seems to be inconclusive.
\section{evolutions to TDD}
\mycomment{I feel that this is a much needed and very interesting section for exploring Agile testing but I am becoming increasingly concerned about how well this section may be able to tie into the rest of the paper. I would like to use this section as a useful resource for seeing where TDD is going/ what problems TDD developers are trying to address/ see if any of these new spin offs may solve problems that are coming up in research listed in section 3. Any input on how to tie this section into the paper or how to better reach the goals given above would be useful.}

As can been seen in the above sections there are some issues in the current implementation of TDD testing.  Due to these issues new methods are starting to appear in the agile community that contain some of TDD's main tenets but have shifted enough away from TDD at some fundamental level that they are starting to receive their own names and classifications.  Although there are many of these spin-offs in TDD for this paper we chose to focus on three more popular spin offs, acceptance test driven development, Behavior driven development, and Agile Specification Driven Development.

\subsection{acceptance test driven development}

@@

\mycomment{need to do research here, specifically it would be useful to do some research on DbC}
\section{conclusion}
In conclusion with the current information available to us there is no obviously superior testing methods between TDD or test first ideologies and waterfall or test last ideologies.  That being said it is worth noting that their are still differences between the two testing methods and that although there is not a clear overall advantage between the two languages certain traits make make one method of testing better then another method of testing in a specific scenario.  For example when dealing with new and relatively inexperienced programmers the test last methodology may be more efficient then the test first methodology.  Another example may be that you believe code coverage is an important necessity for your product, in this case you would probably want to use test first over test last to test your code.  Therefore until research on the subject becomes more clear it would be wise to consider both testing practices as effective and potentially useful for any project you may choose to undertake.

\mycomment{this paragraph is a rough idea of what might be useful conclusions to draw from section three}

For people who are looking to advance the field of TDD it would be potentially very interesting to see how the new TDD spin-offs such as Behavior Driven Development and Agile Specification-Driven Development compare to that of a well documented TDD process like the one suggested for Extreme Programming.  Another thing that could also help advance the field is to do research comparing the effectiveness of waterfall testing and TDD testing between groups with notably different experience levels as some research tentatively points that this may be a relevant variable.

>>>>

\title{The Current State of Test-First vs. Test-Last Testing Draft}

@@

\author{
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
\alignauthor
Chris M. Thomas\\
	\affaddr{Division of Science and Mathematics}\\
	\affaddr{University of Minnesota, Morris}\\
	\affaddr{Morris, Minnesota, USA 56267}\\
	\email{thom3706@morris.umn.edu}
}
\maketitle
\begin{abstract}

When it comes to software development perhaps one of the most important and time consuming processes is that of software testing. In fact, early studies on software testing estimated that software testing could consume fifty percent or more of development costs for a product.  Because of this, the ability to optimize testing to reduce testing costs can be very valuable.  In this paper  we compare two popular methods, test-last testing, often used in waterfall software development methods, and test-first testing, often used in Agile test driven development software development methods, by reviewing recent studies on the subject.  In this review we discuss the possible benefits of test-first and test-last testing and possible problems with the current data comparing these two testing methods.  After that, we explore other methods in test-first testing besides test driven development, such as behavior driven development, in an attempt to find a better test-first testing model.  In the end we discuss our results and potential future studies to help clarify current data.
\end{abstract}

@@

\section{Introduction}
When it comes to software development, perhaps one of the most important and time consuming processes is software testing.  In fact, some early studies on software testing estimated that it could consume fifty percent or more of development costs for a product ~\cite{Bertolino:2007}.  because of this, businesses over time have become increasingly interested in attempting to optimize testing to reduce development costs.

Although there are many testing methods that currently exist, two particular testing methods are currently very popular: test-last testing and test-first testing.  Test-last testing, used mostly in process oriented or waterfall development, is a testing method where testing is done after the software code has been written to ensure that the code works correctly.  Test-first testing, used mostly in interval or agile oriented development, is a testing method where testing is done before the software code is written to ensure that the future code meets certain requirements.

Currently, there is much debate in the testing community about whether or not test first or test last testing is superior.  The goal of this paper is to attempt to give an overview of the current state of this debate by analyzing current research data concerning the advantages and disadvantages of each of these testing methods.  Because research often lags behind current implementations and the field of test-first testing is currently changing due to its relatively new implementation, this paper will also explore where new test-first methods are going and compare them to the research given.  This paper will therefore discuss the advantages and disadvantages of test first testing versus test last testing and explore new emerging test-first methodologies in an attempt to determine the applicability of each methodology.

The rest of the paper is divided into four sections which will discuss the specific ideas above in more detail. In section two of the paper we will discuss what software testing is and current software development models with their supporting testing methods: test-first and test-last testing.  In section three we will provide an analysis of the data explaining the potential advantages and disadvantages of test-first testing compared to test-last testing.  In section four we will go over new test-first based testing methodologies and in section five we will state our conclusions and suggestions for further research in the field.

@@

When it comes to judging the effectiveness of certain testing methods it is important to note that there is no one standard quantitative measurement.  Because of this, many different types of measurement are used in an attempt to prove that one testing methodology is better then another.  Although there are many different attributes that are used for arguing the superiority of one method over another, we will only focus on three attributes that are commonly found throughout research; code coverage, testing time, and code correctness.  Code coverage refers to how many lines of code percent-wise are currently being tested. For example, if I write a test with 70\% test coverage it means that 70\% of the lines of code I wrote are being tested.  Testing time simply means how long it takes to write the actual tests.  Code correctness refers to how many errors are found within code after it is considered finished.  These three attributes are popular to use because they can be quantitatively measured and are considered important within the testing community.

@@

Test last testing is currently a popular testing method and is usually the first testing method that people tend to implement.  Test Last testing is the practice of writing tests after code has been written to check the functionality of the written code.  These tests are then used to check the written code for any potential errors which are then fixed by the developer until no errors are found by the tests.  Test last testing is considered simple to implement and can allow the programmer to focus on writing tests based on areas of his code that he may be concerned about.

@@

In the late 1990s some software developers started to criticize the sequence-oriented waterfall model, complaining that it was too brittle and inflexible to meet the demands of the standard customer.  In response to these critiques of the waterfall model a new model for developing software emerged, the agile development model.  This new development model, based on the tenets of the agile manifesto \mycomment{cite manifesto here!}, promoted the idea that all actions of development should not occur in an ordered sequence but in a series of time-boxed iterations where in each iteration setting requirements, product design, product implementation and product testing would occur simultaneously.  The goal of each iteration is to produce a demonstrable working product to show a customer and receive feedback on the product.  Some current development practices that are considered agile are Extreme Programming and Scrum.

Due to the changes in Agile programming, test-last testing was pushed aside in favor of a different style known as test-first testing.  In 1996 \mycomment{might be 2001} with the release of the agile development practice Extreme Programming, the idea of test first testing, implemented in test driven development, started to become popular for the first time ~\cite{Hammond:2012}. Test-first testing is the practice of writing tests before code has been written and then writing code to make the tests pass.  It should be noted that since tests occur before development test-first testing tends to be heavily linked to development methods and thus the most common test-first models also include development elements as well.

The most well known and most used test-first model is that of test driven development or TDD for short.  In its current use in the field, the phrase TDD is mostly used as a blanket term for any sort of development practice that uses test-first testing to drive code development. That being said it is important to note that although TDD has been turned into a vague term in this paper we will focus more on its original specific definition.  \mycomment{add more once we get to section 3}

\section{Research Data on Test-First vs Test-Last Testing}
In this section we attempt to attempt to obtain useful conclusions between test-first and test-last testing by observing current research articles.  In order to accomplish this we will first start with a data subsection that will go over the three main studies that will be used to draw our conclusions.  Next we will have an analysis subsection that will summarize the results of the study in terms of our three main empirical measurements: code coverage, code correctness, and total development time.  We will then have a discussion subsection that will take about potential issues with summarizing the data given in the research articles and then we shall proceed with a conclusion subsection where we will talk about potential conclusions we can draw from the data.

\subsection{Data}
 In 2012 Lemos et. al ~\cite{Lemos:2012} conducted a study on sixth semester students to see if test-first testing would increase code coverage, increase testing code size, increase code correctness, and/or decrease in total development time in auxiliary functions (functions with 10-200 lines of code) compared to test-Last testing.  In this study 39 sixth semester students, knowledgeable in testing techniques and participants of two 100 minute long test first modules, were asked to complete coding challenges over two sessions.  In the first session, half the students implemented testing-first testing while the other half implemented test-last testing to help solve the problem.  In the second section the students were asked to switch roles and given a different coding challenge.  In order to reduce domain knowledge bias amongst the coding challenges three different challenge question types were handed out at each session.  The results of the study, which were analyzed for statistical significance using the Wilcoxon/Mann-Whitney non-parametric signed-rank paired test, found that test-first testing significantly increased code coverage, testing code size and code development time with no significant increase in code correctness.

In 2010 Kollanus ~\cite{Kollanus:2010} conducted a literary review of TDD.  Using standard literary review methods, Kollanus found and reviewed forty different experiments in scientific journals, magazines, and conference proceedings that provided empirical evidence for TDD.  In the review Kollanus found that the most used measurements in these experiments could be clumped into three measurements: external code quality, internal code quality, and productivity.  In the study Kollanus observed that there was weak support for improved external code quality, very weak support for internal quality, and support for an increased amount of development time.

In 2012 Hellmann et. al conducted a summary on the current status of research of TDD.  Within Hellmann’s background there is a mention of a summary study produced by Jeffries and Mitnik that found in general that TDD largely resulted in an increase in quality, but one study they identified showed instead that TDD resulted in a strong negative impact on quality.  Additionality while they showed that TDD could reduce the amount of effort required by up to 27\%, most studies found an increase in effort of up to 100\%.

\subsection{Analysis}
Two of the three studies covered the topic of code coverage.  In both studies by Kollanus and Lemos et al. it was acknowledged that increased test coverage had occurred in test-first testing methods compared to their test-last counterparts.  All three papers brought up up total development time and noted that test-first testing tended to increase development time, although both Kollanus’s study and Hellmann’s study provide notable contradictory studies to this conclusion.   All three studies in one way or another also brought up code correctness in the form of external code quality in Kollanus or in the form of code quality in the case of Hellmann et al.  In this case the results were across the board where Lemos et al. stated that there was no code correctness difference between test first and test last whereas Kollanus said there was weak evidence that test-first testing produces more correct code then test-last testing.  Hellmann et al provided contradictory evidence backing that in most studies test-first testing has shown better code correctness then test last testing but there was a noted study where test-first testing was less code correct then test-last testing.   In summary, with the studies given, test-first testing produces more code coverage and is likely to take more time to code then test-last testing but due to contradictions in the research given we can not draw a conclusion on code correctness.

\subsection{Discussion}
Many summaries of TDD research ~\cite{Hammond:2012, Hellman:2012, Kettunen:2010} , including the literary review done by Kollanus ~\cite{Kollanus:2010}, have noted that one confounding factor to their ability to summarize the research in the given field of test-first testing has been that many studies are contradictory to one another.  For example in ~\cite{Hellman:2012},  there is a mention of previous summary studies that have had previous issues with conflicting data.  This is then followed by a series of examples of data that has conflicted in other studies in the past.  In Kollanus’s literature review ~\cite{Kollanus:2010} Kollanus points out that many articles in her study contradicted other articles which made it hard to make sound conclusions from the research given and may be a confounding factor in her study.  In most current studies this seems to occur because of two main factors: participant experience and improper study implementation and documentation.

In the case of participant experience there seems to be a skill gap between test first and test last testing.  In an opinion study by ~\cite{Janzen:2007} it was found that a majority college students said they were not comfortable with and had trouble with comprehending TDD, even after doing a coding exercise with it.  The majority of students also said that they were much more comfortable implementing test last methods and would prefer to use test last methods in the future.  Coding professionals, on the other hand, actually preferred test first programming and were much more comfortable with it than students.  They also stated they felt it was relatively easy to understand while students did not. In another opinion study ~\cite{Kettunen:2010}, by Kettunen et al, a common theme throughout the paper was examples of individual testimonies and research conclusions that pointed to test first testing being harder to implement than test last testing.   Considering that most conducted experiments focus on college students and industry professionals, who have vast experience differences, the fact that test first testing may be harder to implement for college students compared to industry professionals may create differing results between studies.   This idea is considered in ~\cite{Hammond:2012} and ~\cite{Kettunen:2010}, but no summary papers where found considering this result and comparing student participant experiment results to professional participant experiment results.

The other problem that has plagued summary papers of test first testing is that most studies either lack documentation in key locations or do not effectively handle the participant conformance issue which comes up in TDD studies.  In the literary review by Kollanus, she acknowledges a frustrating lack of information in many studies on how TDD was implemented.  Most studies, claimed Kollanus, had maybe one or two lines describing their TDD methodology or just simply claimed that they used TDD.  Considering that TDD can be implemented in many ways, as discussed earlier in the background, Kollanus states that the lack of documentation for TDD implementation means that, as a reviewer, she has no idea if the test methods used to produce the results were similar or different thus potentially confounding some of her conclusions.  Another issue similar to this is the conformance issue, brought up in (cite here).  The conformance issue in TDD testing refers to the fact that few researchers make sure that TDD was implemented correctly or at all by its participants.  For example, in the study by Lemos et. al the researchers acknowledged that one of their confounding factors was that they only asked students to write tests before code, thus a variety of different test first methods might have been used within the study making its data less conclusive.   Overall the lack of documentation of how researchers specifically planned to implement TDD in their study and their lack of some sort of monitoring of whether the implementation was actually occurring greatly reduces the credibility of the research being done and allows for confounding factors to potentially occur.

\subsection{Conclusion}

Due to current issues in contradictory data it is hard to make solid conclusions about the advantages and disadvantages of using test first testing instead of test last testing.  What can be done instead is we can consider certain trends in research that can suggest potential answers.  Most studies and summaries seem to agree that test-first testing tends to produce more test coverage compared to test-last testing and that test first testing tends to take longer to write tests compared to test first testing.  Two of the studies we looked at, the experiment by lemos and the literary review by Kollanus, point out these two trends.  Also one or both trends have been noted through multiple papers ~\cite{Kettunen:2010, Hammond:2012, Hellman:2012} with no major contradictions found.  Another convincing trend that has occurred is that in general test first testing seems to be harder to implement than test last testing as mentioned earlier.   Although these trends seem to be clear, the rest seem to be more muddled.  Code correctness for example seems to have no clear trend as multiple studies have reached contradictory conclusions to other studies.  Another hot button topic that fails to show a trend one way or the other is the amount of time spent simply developing code as this again seems to have results across the board.  From these trends we can consider that test first testing overall probably takes more time to write, increases code coverage, and is harder to implement than test-last testing and that other advantages or detriments may exist but they are unclear in current research.

\section{evolutions to TDD}
\mycomment{this section is currently a work in progress}

As can been seen in the above sections there are some issues in the current implementation of TDD testing.  Due to these issues new methods are starting to appear in the agile community that contain some of TDD's main tenets but have shifted enough away from TDD at some fundamental level that they are starting to receive their own names and classifications.  Although there are many of TDD spin-offs, for this paper we chose to focus on three more popular spin offs, acceptance test driven development, Behavior driven development, and Agile Specification Driven Development.

\subsection{Test Driven Development}
Test driven development, as mentioned earlier is currently the most widely used test first testing and design methodology.  Although in the previous cases we have been using TDD as a vague term in this section we will focus on the the original TDD methodology introduced in Extreme Programming.  In the original TDD methodology the developer repeats a step of processes to develop his code.  The process begins once all current tests pass or the new code has just been started.  When this occurs the programmer writes a new failing test that tests the simplest functionality the programmer wishes to add to their code.  Once the test has been written and the test fails, the programmer then writes the minimal amount of code to make the test pass.  After this step the programmer proceeds to refactor any clutter within his solution and then repeats the process until the code is complete.

Although TDD is a very popular style of test first testing, it should be noted that a perceived weakness to the TDD methodology exists.  The main issue many people have with test driven development is that it fails to suggest a style of testing and how to best define an independent functionality in ones code plan.  In the study ~\cite{Kettunen:2010} (cite others here as needed) people noted that TDD was difficult because they had a hard time deciding how to implement their tests effectively.  Another related issue noted in ~\cite{Kettunen:2010} was that some individuals found it hard to figure out what needed to specifically be tested thus some found they wrote an overabundance of tests causing the process to become inefficient and thus take more time.  Others found that focusing on the simplest functions first left serious potential problems to the end of development causing a serious time crunch problem for product release.  Due to these issues with defining functionality and other issues within TDD new methods for implementing test first testing are being designed and implemented in an attempt to solve these problems.
\subsection{Acceptance Test Driven Development}

@@

\mycomment{need to do research here, specifically it would be useful to do some research on DbC}

\subsection{section conclusion}
\mycomment{the goal here is to have a discussion over which TDD spin off might be most promising and for what reasons}

\section{conclusion}
\mycomment{this section is currently a work in progress}
\subsection{Conclusion intro}

In this paper we talked about two common test methods: test-first testing, often found in waterfall development models and test-last testing, often found in agile development models.  In section two we defined these test methods as well as provided background information to the reader.  In section three we explored recent research into the comparison of the two different testing methods and explored potential research problems with the current data.  In particular we found that data was contradictory but we still were able to tentatively conclude that test-first testing increases test coverage, increases time taken to test, and is harder to implement than test-last testing.  In this section we also suggested two potential reasons for the contradictory data: different participant experience levels and poor documentation/implementation of specific test first methods. In section four we explored different implementations of test first testing.

\subsection{Discussion of Implications of Section 3}
\mycomment{stubbed for now}

\subsection{Discussion of Implications of Section 4}
\mycomment{stubbed for now}
\subsection{Suggestion for Further Research}
For people who are looking to advance the field of TDD it would be potentially very interesting to see how the new TDD spin-offs such as Behavior Driven Development and Agile Specification-Driven Development compare to that of a well documented TDD process like the one suggested for Extreme Programming.  Another useful study that could be implemented would be to compare the results of studies thing that could also help advance the field is to do research comparing the effectiveness of waterfall testing and TDD testing between groups with notably different experience levels as some research tentatively points that this may be a relevant variable.
